Ecuador plant trait TRY Cleaning

### 2022-11-16 code/L1/L1_Ecuador_plants_TRY.Rmd
Add code to transform dataframe to wide table

# Explore data
```{r}
TRYdata_explore_trait <- rtry_explore(try_data, TraitID, TraitName)
View(TRYdata_explore_trait)
```

>>>>

# Transform to wide table
```{r}
#-------------------------------------------------
# Exclude
# 1. All entries with "" in TraitID
# 2. Potential categorical traits that don't have a StdValue
# 3. Traits that have not yet been standardized in TRY
# Then select the relevant columns for transformation
# Note: The complete.cases() is used to ensure the cases are complete,
#       i.e. have no missing values
#-------------------------------------------------
num_traits <- rtry_select_row(try_data, complete.cases(TraitID) & complete.cases(StdValue))
num_traits <- rtry_select_col(num_traits, ObservationID, AccSpeciesID, AccSpeciesName, TraitID, TraitName, StdValue, UnitName)
# Extract the unique value of latitude (DataID 59) and the corresponding ObservationID
workdata_lat <- rtry_select_anc(try_data, 59)

# Extract the unique value of longitude (DataID 60) and the corresponding ObservationID
workdata_lon <- rtry_select_anc(try_data, 60)

# To merge the extracted ancillary data with the numerical traits
# Merge the relevant data frames based on the ObservationID using rtry_join_left (left join)
num_traits_georef <- rtry_join_left(num_traits, workdata_lat, baseOn = ObservationID)
num_traits_georef <- rtry_join_left(num_traits_georef, workdata_lon, baseOn = ObservationID)

# Perform wide table transformation on TraitID, TraitName and UnitName
# With cell values to be the mean values calculated for StdValue
num_traits_georef_wider <- rtry_trans_wider(num_traits_georef, names_from = c(TraitID, TraitName, UnitName), values_from = c(StdValue), values_fn = list(StdValue = mean))
```
